### 2024-12-04 manuscript.tex
Addressing comments

nextGEMS is a project \citep{nextgems} focused on the
research and development of GSRMs at multiple modelling centres and
universities in Europe.  The project also develops GSRM versions of the
Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \cite{hohenegger2023}), the Integrated
Forecasting System (IFS), and their ocean components at eddy-resolving
resolutions: ICON-O coupled with ICON and Finite-Element/volumE Sea ice-Ocean
Model (FESOM) and Nucleus for European Modelling of the Ocean (NEMO) coupled
with IFS.  The project has so far produced ICON and IFS simulations with three
development versions called Cycle 1--3 and a pre-final version, with a final production
version planned by the end of the project. nextGEMS is not the only project
developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in
development include: Convection-Permitting Simulations With the E3SM Global
Atmosphere Model [SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM;
\cite{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
modeling for Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de
Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
\cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
Sphere [FV3, \cite{lin2004}], the National Aeronautics and Space Administration
(NASA) Goddard Earth Observing System global atmospheric model version 5
[GEOS5; \cite{putman2011}], Model for Prediction Across Scales [MPAS;
\cite{skamarock2012}], and System for Atmospheric Modeling [SAM;
\cite{khairoutdinov2003}].

>>>>

nextGEMS is a project \citep{nextgems} focused on the
research and development of GSRMs at multiple modelling centres and
universities in Europe.  The project also develops GSRM versions of the
Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \cite{hohenegger2023}), the Integrated
Forecasting System [IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
resolutions: ICON-O \citep{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean
Model [FESOM; \cite{wang2014}] and Nucleus for European Modelling of the Ocean [NEMO; \cite{madec2023}] coupled
with IFS.  The project has so far produced ICON and IFS simulations with three
development versions called Cycle 1--3 and a pre-final version, with a final production
version planned by the end of the project. nextGEMS is not the only project
developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in
development include: Convection-Permitting Simulations With the E3SM Global
Atmosphere Model [SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM;
\cite{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
modeling for Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de
Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
\cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
Sphere [FV3, \cite{lin2004}], the National Aeronautics and Space Administration
(NASA) Goddard Earth Observing System global atmospheric model version 5
[GEOS5; \cite{putman2011}], Model for Prediction Across Scales [MPAS;
\cite{skamarock2012}], and System for Atmospheric Modeling [SAM;
\cite{khairoutdinov2003}].
